From Education to Entrepreneurship

### 2014-12-04 index.Rmd
Try to set panels

set.seed(123)
Dropped4=data.frame(A=rpois(100, 20),
             B=rpois(100, 5),
             C=rpois(100, 50))
print( 
  gvisHistogram(Dropped4, options=list(
    legend="{ position: 'top', maxLines: 2 }",
    colors="['#5C3292', '#1A8763', '#871B47']",
    width=600, gvis.plot.tag = 'chart'),
    chartid="Histogram")
)
```

>>>>

set.seed(123)
Dropped4=data.frame(A=rpois(100, 20),
             B=rpois(100, 5),
             C=rpois(100, 50))

print( 
  gvisHistogram(Dropped4, options=list(
    legend="{ position: 'top', maxLines: 2 }",
    colors="['#5C3292', '#1A8763', '#871B47']",
    width=600, gvis.plot.tag = 'chart'),
    chartid="Histogram")
)
